### 2023-10-30 state/lstm.tex
Correcting inappropriate raccourcis and correcting design
Removed a todo
Worked on paper+corrected errors

The first \ac{LSTM} was invented in 1997 by Hochreiter and Schmidhuber \cite{firstLSTM}. \acp{LSTM} changed a lot through the years to become what they are now.

\acp{LSTM} was created to fix the vanishing gradient problem. \acp{LSTM} alleviate this issue by adding a cell state, this state gives it the ability to choose what input is important and which one is not, thus giving it a long term memory. This ability gave the uncommon name of \acl{LSTM} as it has both long and short term memory. This is what makes \acp{LSTM} adequate for sequence data. They can analyze the data and keep the information from the last time step to make a better decision afterwards. The most comprehensible example is considering a sentence. %TODO : find example)

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}
  \label{fig:lstmCell}
  \caption{\acs{LSTM} cell, adapted from \cite{wikiLSTM}}
\end{figure}

\Cref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then activated with either a \ac{tanh} or a sigmoid activation function. Each input to the cell is a vector.
Those vectors are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden states (sometimes referred to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

The equations that haven't been rewritten simply stay the same.

@@

Once again, the equations that haven't been rewritten are unchanged.

>>>>

The first \ac{LSTM} was invented in 1997 by Hochreiter and Schmidhuber \cite{firstLSTM}. \acp{LSTM} changed a lot through the years to become what they are now \cite{improvLSTM}.

\acp{LSTM} was created to fix the vanishing gradient problem. \acp{LSTM} alleviate this issue by adding a cell state, this state gives it the ability to choose what input is important and which one is not, thus giving it a long term memory. This ability gave the uncommon name of \acl{LSTM} as it has both long and short term memory. This is what makes \acp{LSTM} adequate for sequence data. They can analyze the data and keep the information from the last time step to make a better decision afterwards. The most comprehensible example is considering a sentence.

@@

\begin{figure}[H]
  \centering
  \includesvg[width=\textwidth,pretex=\large]{lstm/lstmCell.svg}
  \caption{\acs{LSTM} cell, adapted from \cite{wikiLSTM}}
  \label{fig:lstmCell}
\end{figure}

\Cref{fig:lstmCell} shows the complexity of the \ac{LSTM} architecture. In an \ac{LSTM}, each gate is a different \ac{NN} and then acivated with either a \ac{tanh} or a sigmoid activation function. Each input to the cell is a vector.
Those vectors are of varying sizes depending on several factors. For example, both $h_t$ and $c_t$ are of the same size as the number of hidden states (sometimes referred to as cell state) for any $t\geq 0$.
The input vector ($x_t$) is of size of the sample we want to feed for each time step.

@@

The equations that have not been rewritten simply stay the same.

@@

Once again, the equations that have not been rewritten are unchanged.
